### 2023-11-15 let.tex
Add reference to pattern matching with holes paper

>>>>

Recent work by \citet{yuan2023} addresses the problem of general pattern matching with typed holes,
providing mechanisms to reason statically about redundancy and exhaustiveness in the presence of
pattern holes. A comprehensive account incorporating the marked lambda calculus would employ error
marks indicating inexhaustive matches and redundant patterns.
